The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-10 paper/paper.tex
add JaxCNN and JaxResNet

\subsection{ {\sc CNN} } 
This method uses an optimized Convolutional Neural Network (CNN) to assign
galaxies to redshift bins.

@@

\subsection{ {\sc JaxCNN} }

\subsection{ {\sc JaxResNet} }

@@

\subsection{ {\sc funbins} }
This method uses the random forest algorithm described in section \ref{randomforest} to assign galaxies to tomographic bins. There are 3 options for determining the bins used to assign labels to the training data - \textit{log}, \textit{random}, and \textit{chi}.

@@

Once the bin edges are determined by either of the methods above, the random forest is trained as described in section \ref{randomforest}.

>>>>

\subsection{ {\sc CNN} } \label{sec:cnn}
This method uses an optimized Convolutional Neural Network (CNN) to assign
galaxies to redshift bins.

@@

\subsection{{\sc JaxCNN \& JaxResNet} }

This methi submitted by the author AP.

JaxCNN and JaxResNet are a convolutional neural network based algorithm that
maps the relationship between the color-magnitude data of galaxies to their bin
indices. Convolutional neural network (CNN) models, as described in section
\ref{sec:cnn}, consist of several layers, each consisting of a linear
convolution operator followed by polling layers and a nonlinear activation
function. Residual Network (ResNet) models take one step further and learn the
\textit{identity} mapping by skipping, or adding \textit{shortcut} connections
to, one or more layers \citep{resnet}. ResNet helps solve the vanishing gradient
problem, hence we can have a deeper neural network.

JaxCNN uses 2-layer convolutional neural networks and JaxResNet uses a stack of
3 layers consisting of $1 \times 1, 3 \times 3$, and $1 \times 1$ convolutions
with shortcut connections added to each stack. Both methods use the Rectified
Linear Unit (ReLU) activation function under the ADAM optimizer \cite{adam} with
a learning rate of 0.001.

We chose the learning algorithm for both methods to minimize the reciprocal of
the figure of merit $F$, where $F$ is defined in eqref{E:FOM}. We implement
these models using the JAX-based Flax neural network library \cite{jax}.

@@

\subsection{ {\sc funbins} }
This method uses the random forest algorithm described in section \ref{sec:randomforest} to assign galaxies to tomographic bins. There are 3 options for determining the bins used to assign labels to the training data - \textit{log}, \textit{random}, and \textit{chi}.

@@

Once the bin edges are determined by either of the methods above, the random forest is trained as described in section \ref{sec:randomforest}.
